`tidyfun`

### 2020-01-13 papers.Rmd
update 2020-01-13

@@

E. A. Gibson, **J. Goldsmith**, and M.-A. Kioumourtzoglou (2019+).
Complex Mixtures, Complex Analyses: an Emphasis on Interpretable Results.
<i> Current Environmental Health Reports, </i> 
accepted.
[[Link](https://link.springer.com/article/10.1007%2Fs40572-019-00229-5)]

E. A. Gibson, Y. Nunez, A. Abuawad, A. R. Zota, S. Renzetti, K. L. Devick, C. Gennings, **J. Goldsmith**, B. A. Coull, and M.-A. Kioumourtzoglou. (2019)
An overview of methods to address distinct research questions on environmental mixtures: an application to persistent organic pollutants and leukocyte telomere length.
<i> Environmental Health, </i> 
<b>18</b> ???.
[[Link](https://ehjournal.biomedcentral.com/articles/10.1186/s12940-019-0515-1)
| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/31462251)
| Article selected as NIEHS [Extramural Paper of the Month](https://factor.niehs.nih.gov/2019/11/papers/dert/index.htm)]

@@

Y. Chen<sup>&#8225;</sup>, **J. Goldsmith**, and R. T. Ogden (2019).
Nonlinear mixed-effects models for PET data.
<i> Transactions on Biomedical Engineering, </i> 
<b>66</b> 881-891.
[[Link](https://ieeexplore.ieee.org/document/8424003/)]

@@

@@

J. Lee<sup>&#8225;</sup>, G. Li, W. F. Christensen, G. Collins, M. Seeley, A. E. Bowden, D. T. Fullwood, and **J. Goldsmith** (2018). 
Functional Data Analyses of Gait Data Measured Using In-Shoe Sensors. 
<i> Statistics in Biosciences, </i> 
accepted.

J. A. Woo Baidal, K. Morel, K. Nichols, E. Elbel, N. Charles, **J. Goldsmith**, L. Chen, and E. M. Taveras (2018+). 
Sugar-sweetened beverage attitudes and consumption during the first 1,000 days of life. 
<i> American Journal of Public Health, </i> 
accepted.

J. Wrobel<sup>&#8225;</sup>, V. Zipunnikov, J. Schrack, and **J. Goldsmith** (2018+).
Registration for exponential family functional data.
<i> Biometrics, </i> 
accepted.

Y. Chen<sup>&#8225;</sup>, **J. Goldsmith**, and R. T. Ogden (2018+).
Functional data analysis of dynamic PET data.
<i> Journal of the American Statistical Association, </i> 
accepted.

D. Backenroth<sup>&#8225;</sup>, **J. Goldsmith**, M. D. Harran, J. C. Cortes, J. W. Krakauer, and T. Kitago (2018+).
Modeling motor learning using heteroskedastic functional principal components analysis.
<i> Journal of the American Statistical Association, </i> 
accepted.
[[PDF](resources/HetFCPA.pdf)]

>>>>

## 2020

D. Backenroth<sup>&#8224;</sup>, R. T. Shinohara, J. A. Schrack, and **J. Goldsmith** (2020+).
Non-negative decomposition of functional count data. 
<i> Biometrics, </i>  accepted.

A. E. Margolis, J. Broitman, J. M. Davis, L. Alexander, A. Hamilton, Z. Liao, S. Banker, L. Thomas, G. A. Salum, K. Merikangis, **J. Goldsmith**, T. Paus, K. Keyes, M. P. Milham (2020+).
Prevalence Of Nonverbal Learning Disability In Three Community Samples
<i> JAMA Network Open, </i> accepted.

D. Pagliaccio et al (2020+).
Prenatal Exposure to Polycyclic Aromatic Hydrocarbons Modifies the Effects of Early Life Stress on Attention & Thought Problems in Late Childhood.
<i> The Journal of Child Psychology and Psychiatry,, </i> accepted.

@@

E. A. Gibson, Y. Nunez, A. Abuawad, A. R. Zota, S. Renzetti, K. L. Devick, C. Gennings, **J. Goldsmith**, B. A. Coull, and M.-A. Kioumourtzoglou. (2019)
An overview of methods to address distinct research questions on environmental mixtures: an application to persistent organic pollutants and leukocyte telomere length.
<i> Environmental Health, </i> 
<b>18</b> 76.
[[Link](https://ehjournal.biomedcentral.com/articles/10.1186/s12940-019-0515-1)
| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/31462251)
| Article selected as NIEHS [Extramural Paper of the Month](https://factor.niehs.nih.gov/2019/11/papers/dert/index.htm)]

R. Kundert, **J. Goldsmith**, J. Veerbeek, J. W. Krakauer, and A. R. Luft (2019). 
What the proportional recovery rule is (and is not): methodological and statistical considerations.
<i>Neurorehabilitation and Neural Repair, </i> 
<b>33</b> 876-887.
[[Link](https://journals.sagepub.com/doi/full/10.1177/1545968319872996)
| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/31524062)]

A.G. Rundle, D. Gallagher, J. B. Herbstman, **J. Goldsmith**, D. Holmes, A. Hassoun, S. Oberfield, R. L. Miller, H. Andrews, E. M. Widen, L. A. Hoepner, and F. Perera (2019). 
Prenatal Exposure to Airborne Polycyclic Aromatic Hydrocarbons and Childhood Growth Trajectories from Age 5 to 14 Years.
<i>Environmental Research, </i> 
<b>177</b> 108595.
[[Link](https://www.sciencedirect.com/science/article/abs/pii/S0013935119303925)
| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/31352299)]

J. Lee<sup>&#8225;</sup>, G. Li, W. F. Christensen, G. Collins, M. Seeley, A. E. Bowden, D. T. Fullwood, and **J. Goldsmith** (2019). 
Functional Data Analyses of Gait Data Measured Using In-Shoe Sensors. 
<i> Statistics in Biosciences, </i> 
<b>11</b> 288-313.
[[Link](https://link.springer.com/article/10.1007/s12561-018-9226-3)]

E. A. Gibson, **J. Goldsmith**, and M.-A. Kioumourtzoglou (2019+).
Complex Mixtures, Complex Analyses: an Emphasis on Interpretable Results.
<i> Current Environmental Health Reports, </i> 
accepted.
[[Link](https://link.springer.com/article/10.1007%2Fs40572-019-00229-5)]
| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/31069725)]

Y. Chen<sup>&#8225;</sup>, **J. Goldsmith**, and R. T. Ogden (2019).
Functional data analysis of dynamic PET data.
<i> Journal of the American Statistical Association, </i> 
<b>114</b> 595-609.
[[Link](https://www.tandfonline.com/doi/abs/10.1080/01621459.2018.1497495)
| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/31447493)]

@@

J. Wrobel<sup>&#8225;</sup>, V. Zipunnikov, J. Schrack, and **J. Goldsmith** (2019).
Registration for exponential family functional data.
<i> Biometrics, </i> 
<b>75</b> 48-57.
[[Link](https://onlinelibrary.wiley.com/doi/full/10.1111/biom.12963)]

@@

Y. Chen<sup>&#8225;</sup>, **J. Goldsmith**, and R. T. Ogden (2019).
Nonlinear mixed-effects models for PET data.
<i> Transactions on Biomedical Engineering, </i> 
<b>66</b> 881-891.
[[Link](https://ieeexplore.ieee.org/document/8424003/) 
| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/30072311)]

@@

D. Backenroth<sup>&#8225;</sup>, **J. Goldsmith**, M. D. Harran, J. C. Cortes, J. W. Krakauer, and T. Kitago (2018).
Modeling motor learning using heteroskedastic functional principal components analysis.
<i> Journal of the American Statistical Association, </i> 
<b>113</b> 1003-1015.
[[Link](https://www.tandfonline.com/doi/abs/10.1080/01621459.2017.1379403) 
| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/30416231)]

J. A. Woo Baidal, K. Morel, K. Nichols, E. Elbel, N. Charles, **J. Goldsmith**, L. Chen, and E. M. Taveras (2018+). 
Sugar-sweetened beverage attitudes and consumption during the first 1,000 days of life. 
<i> American Journal of Public Health, </i> 
<b>108</b> 1659-1665.
[[Link](https://ajph.aphapublications.org/doi/abs/10.2105/AJPH.2018.304691) 
| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/30359102)]
